Bayesian Neural Networks

### 2024-03-21 Paper/paper.tex
Removing old work

\documentclass[12pt]{article}
\usepackage{fancyhdr}     % Enhanced control over headers and footers 
\usepackage[T1]{fontenc}  % Font encoding
\usepackage{mathptmx}     % Choose Times font 
\usepackage{microtype}    % Improves line breaks      
\usepackage{setspace}     % Makes the document look like horse manure 
\usepackage{hyperref}
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = black, %Colour of internal links
	citecolor   = black %Colour of citations
}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{endnotes}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage{rotating}

@@

\title{Bayesian Neural Networks}
\author{
	Blair, Taylor\\
	\and
	Ava\\
	\and
	Conor\\
}
\date{\today}
\let\footnote=\endnote

@@

\pagestyle{fancy} % Default page style 
\lhead{Taylor Blair}
\chead{}
\rhead{\thepage}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\renewcommand{\theendnote}{\Roman{endnote}}

@@

Merkle trees are used as authenticated data structures with optimal complexity for proving membership and comparing against other structures.

\subsection{Bitcoin} \label{sec:Bitcoin}

Bitcoin, and other cryptocurrencies, use Merkle trees for the commitment header.  The \textit{chain} in blockchain refers to the chain of receipts from processed transactions. It would be too slow to create a receipt for each transaction, so Bitcoin groups transactions into sections. The smaller group of transactions is a Merkle tree where the leaf nodes represent a single transaction. Thus the group of transactions results in a root hash which is used as the commitment header.

Merkle trees were incorrectly implemented in the Bitcoin protocol. This implementation resulted in DOS attacks due to over-hashing and duplicate nodes (CVE-2012-2459). This bug was patched in a proposal that replaced the Merkle tree implementation\cite{friedenbach_alm_2017}.

\subsection{BitTorrent Data Integrity} \label{sec:BitTorrent}

BitTorrent uses Merkle trees for checking the integrity of torrented files. The torrented data is hashed into a Merkle Tree and the root hash is compared with a trusted peer to verify integrity\cite{bep30}. If the root hashes do not match then the nodes below are compared with the trusted peer. This process repeats until a non-matching block is reached. The advantage of using a Merkle tree over another data structure is finding corrupted data blocks in $O(\log(n))$ time.

>>>>

\documentclass[12pt]{article}
\usepackage{fancyhdr}     % Enhanced control over headers and footers 
\usepackage[T1]{fontenc}  % Font encoding
\usepackage{mathptmx}     % Choose Times font 
\usepackage{microtype}    % Improves line breaks      
\usepackage{setspace}     % Makes the document look like horse manure 
\usepackage{hyperref}
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = black, %Colour of internal links
	citecolor   = black %Colour of citations
}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{endnotes}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage{rotating}

@@

\title{Bayesian Neural Networks}
\author{
	Blair, Taylor
	\and
	Sorgmon, Ava
	\and
	Conor
}
\date{\today}
\let\footnote=\endnote

@@

\pagestyle{fancy} % Default page style 
\lhead{Blair, Sorgman, Conor}
\chead{}
\rhead{\thepage}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\renewcommand{\theendnote}{\Roman{endnote}}

@@

...
